Improving the modelling of tempo and phoneme duration

### 2017-04-05 Paper/Paper_v1.tex
some more changes to sr
some adds to chapter basics

\chapter{Fundamentals}
\section{Data Mining}
Data Mining means in foreground looking for patterns in data with the help of computers. Patterns are helpful for humans to understand data. They reduce the amount of data, and of available features to the relevant ones. Computers help process within resonable time amounts of data that would need years of manual processing.
\section{Machine Learning}
Machine Learning means building a program or model which can make predictions about an unseen dataset, like filling in missing information, based on data mining results from a given dataset. 
\section{Preparing the Data}
A very important and time consuming step in data mining is data preparation, which is the next step after data collection. At this stage one needs to asses the quality of the data, expressed as noise ratio, and strategies for dealing with it. If the data used has been originally collected for another purpose, then it needs to be assessed in terms of features it contains, actually needed features, and organization resp. reorganization of data to serve new purpose.

@@

@@

%\begin{table}[htbp]
%\caption {Duration of long vowels vs. speech rate calculated at turn, phrase, and word level} 
%\centering
\vspace{10mm}
\begin{tabular}{|l|l|}
\hline
Segment	 & Correlation coefficient (Pearson)\\
\hline
\hline
Turn 		&0.727178570436 \\
	\hline
Phrase  &\\
	\hline
Word  &  0.794901825792\\
	\hline
\end{tabular}
%\end{table}

%\end{table}

>>>>

\chapter{Basics}
\section{Data Mining}
Data Mining means in foreground looking for patterns in data with the help of computers. Patterns are helpful for humans to understand data. They reduce the amount of data, and of available features to the relevant ones. Computers help process within resonable time amounts of data that would need years of manual processing.

\section{Machine Learning}
Machine Learning means building a program or model which can make predictions about an unseen dataset, like filling in missing information, based on data mining results from a given dataset. It consists of a so-called training phase, in which the training data is being processed by the selected machine learning method and hypotheses or models are formed. These can then be used to make predictions about new data. The training data consists of a set of instances, each of them being described by a feature vector. The training phase is followed by an evaluation phase, in which predictions about unseen data are being made and compared to the actual values.

We used machine learning to solve a task involving both classification and numeric prediction. We used for this two model tree methods: M5P and REPTree. The reasons we chose them is because trees are easy to interpret, they can perform both classification and numeric prediction tasks, we could easily generate them using Weka, and are the closest to classification and regression (CART) trees, also used in the literature \cite{Brinckmann2003} for phoneme duration prediction, so we have data to compare with.

\subsection{REPTree}

\subsection{M5P}
The M5P model tree is a decision tree based on the M5 algorithm introduced by Quinlan (1992). It

\section{Preparing the Data}
A very important and time consuming step in data mining is data preparation, which is the next step after data collection. At this stage one needs to asses the quality of the data, expressed as noise ratio, and strategies for dealing with it. If the data used has been originally collected for another purpose, then it needs to be assessed in terms of features it contains, actually needed features, and organization resp. reorganization of data to serve new purpose.

@@

\section{Tools}

@@

\begin{table}[htbp]
\caption {Duration of long vowels vs. speech rate calculated at turn, phrase, and word level} 
%\centering
\vspace{10mm}
\begin{tabular}{|l|l|c|}
\hline
Segment	 & Formula & Correlation coefficient (Pearson)\\
\hline
\hline
Turn 		& $turn\_dur / phon\_count$ &0.727178570436 \\
	\hline
	&  $phon\_count / turn\_dur$ & -0.270392865503 \\
	\hline
Phrase  & $phrase\_dur / phon\_count$ & 0.561266362391\\
	\hline
	&  $phon\_count / phrase\_dur$ & -0.377058296098\\
	\hline
Word  & $word\_dur / phon\_count$ &  0.794901825792\\
	\hline
	&  $phon\_count / phrase\_dur$ & -0.616539202577\\
	\hline
\end{tabular}
\end{table}

\begin{figure}[htbp]
\centering
	\begin{subfigure}[h]{0.48\textwidth}
	\centering
	\includegraphics[width=\textwidth]{../Graphen/SR_turn.eps}
	\label{fig:tsr}
	\end{subfigure}
\hfill
	\begin{subfigure}[h]{0.48\textwidth}
	\centering
	\includegraphics[width=\textwidth]{../Graphen/SR0.eps}
	\label{fig:phraseSR}
	\end{subfigure}
\hfill
	\begin{subfigure}[h]{0.48\textwidth}
	\centering
	\includegraphics[width=\textwidth]{../Graphen/SR4.eps}
	\label{fig:wsr}
	\end{subfigure}
\caption[Speech rate vs long vowel duration]{Phoneme durations measured in msec plotted against different speech rates.}
\label{fig:SR_corr}
\end{figure}
